Leveraging Diversity to Find Bugs in JavaScript Engines

### 2019-02-14 paper/paper.tex
pass on mining tests

\sloppy{}We observed that issue trackers are an important source of
test data and should not be ignored. Analyzing a sample of issues, we
observed that developers either 1) add test cases as attachments of
issues or 2) embed test cases within the textual description of an
issue. The test cases in attachments are longer compared to the test
cases embedded in issue descriptions whereas the latter are more
common. Consequently, we thought we should handle both
cases. Accessing attachments is simpler compared to embedded
tests. For attachments, we wrote a crawler to visit the issue trackers
of all four engines listed in Table~\ref{tab:engines} and were able to
retrieve a total of \Fix{XX} files
(\jsc{}=\Fix{XX},\veight{}=\Fix{XX},\chakra{}=\Fix{XX}, and
\smonkey{}=\Fix{XX}). To mine tests from the textual descriptions, we
broke the text describing the issue in paragraphs and used a binary
classifier to label each paragraph as ``code'' or ``not code''. Then,
based on that information, we merged consecutive paragraphs labeled as
``code'' and used a \js\ parser to check well-formedness of the
corresponding code fragment. Using that method we were able to
retrieve a total of \Fix{XX} files
(\jsc{}=\Fix{XX},\veight{}=\Fix{XX},\chakra{}=\Fix{XX}). All those
files were included in Table~\ref{tab:test-suites}.

>>>>

\sloppy{}We observed that issue trackers are an important source of
test data and should not be ignored. Analyzing a sample of issues, we
observed that developers either 1) add test cases as attachments of
issues or 2) embed test cases within the textual description of an
issue. The test cases in attachments are longer compared to the test
cases embedded in issue descriptions whereas the latter are more
common. Consequently, we thought we should handle both
cases. Accessing attachments is simpler compared to embedded
tests. For attachments, we wrote a crawler to visit the issue trackers
of all four engines listed in Table~\ref{tab:engines} and were able to
retrieve a total of 627 files
(\jsc{}=147,\veight{}=370 and
\smonkey{}=110). To mine tests from the textual descriptions, we
broke the text describing the issue in paragraphs and used a binary
classifier to label each paragraph as ``code'' or ``not code''. Then,
based on that information, we merged consecutive paragraphs labeled as
``code'' and used a \js\ parser to check well-formedness of the
corresponding code fragment. Using that method we were able to
retrieve a total of \Fix{XX} files
(\jsc{}=\Fix{XX},\veight{}=\Fix{XX},\chakra{}=\Fix{XX}). All those
files were included in Table~\ref{tab:test-suites}.
